### 2025-04-13 basic-statistics.qmd
20250413 - update frame size

```{=html}
<iframe id="distributionVisualizer" src="https://ffashiny.shinyapps.io/distributionvisualizer/" style="border: none; width: 100%; height: 720px" frameborder="0"></iframe>
```

>>>>

```{=html}
<iframe id="distributionVisualizer" src="https://ffashiny.shinyapps.io/distributionvisualizer/" style="border: none; width: 100%; height: 1000px" frameborder="0"></iframe>
```
